---
title: "conference_program_koichi"
format: pdf
editor: visual
---

## Conference: Latin American PolMeth III (2019)

```{r}
library(pdftools)
polmeth <- pdf_data("https://polmeth.org/files/files/polmeth/files/2019-latin-polmeth.pdf", font_info = TRUE)
polmeth[[1]]
```

```{r}
# a workshop
polmeth[[1]] |> 
  filter(str_detect(text, "Workshop"))

# a paper title
polmeth[[1]] |> 
  filter(str_detect(text, "Socio"))

# a speaker name
polmeth[[1]] |> 
  filter(str_detect(text, "Matías"))

# there are no co-authors in this conference

# a word in the right column
polmeth[[1]] |> 
  filter(str_detect(text, "Police"))

# a word on the right edge of the left column
polmeth[[1]] |> 
  filter(str_detect(text, "capacity"))
```

## Combining the columns

```{r}
tidy_page <- function(page) {
  left_column <- page |> 
    filter(x < 350) |> 
    group_by(y) |> 
    summarise(text = paste(text, collapse = " "),
              font_name = list(unique(font_name)))
  
  right_column <- page |> 
    filter(x > 350) |> 
    group_by(y) |> 
    summarise(text = paste(text, collapse = " "),
              font_name = list(unique(font_name)))
  
  bind_rows(left_column, right_column)
    
}
```

## Finding and using patterns

```{r}
polmeth_data <- polmeth[1:2] |> 
  # bring the text in the correct order on each page
  map(tidy_page) |> 
  bind_rows() |> 
  # paper titles use a specific font, which make them easy to identify
  mutate(paper_title = font_name == "Calibri")
  # Panels start with the string panel and a large bold font
  mutate(workshop_start = font_name == "Comfortaa-Bold" & str_detect(text, "Workshop")) |> 
  # using cumsum, we count the TRUE values. One appears at the start of each panel
  mutate(workshop = cumsum(workshop_start)) |> 
  # we are not interested in the information before the first panel
  filter(workshop > 0) |> 
  group_by(workshop) |> 
  # we can count the first appearance of a paper title to give the paper a unique id per panel
  mutate(paper_nr = cumsum(paper_title & !lag(paper_title))) |> 
  # now we can group the data using this id to make sure the authors are matched to the right paper
  group_by(workshop, paper_nr) |> 
  # summarised takes several elements and uses a function to return exactly one
  summarise(
    # we select all text where the paper_nr == 0, which is te panel title
    workshop_title = paste(text[paper_nr == 0], collapse = " "),
    # now we combine the text in the rows that have a paper title
    workshop_title = paste(text[paper_title], collapse = " "),
    # finally, we put the authors in a list. They are the text within a panel descript that uses one of two fonts
    author = list(text[font_name %in% "Calibri-Italic"]),
    .groups = "drop"
  ) |> 
  # we replace empty rows with NAs so we can fill them with the preeeding text
  mutate(across(workshop_title:paper_title, function(x) ifelse(x == "", NA_character_, x))) |> 
  fill(workshop_title) |> 
  filter(paper_nr > 0) |> 
  unnest(author)
polmeth_data
```

Comments:
I am stuck with the paper names, because they are squeezed into cells and with line breaks.
Thus, the current code considers each line as a different paper. What could be done to fix this?

Also, when running the current code, I get an error saying that R could not subset a column that does not exist (referring to "paper_title".
However, that column was set at the beginning of this chunk.
